\section{Battery Software Engineer - Controls}

My name is Cole Fuerth, and I have been excited about the new Stellantis plant since it has been announced. I feel I am qualified and an ideal candidate as a software engineer for a BMS. I am a Computer Science student at the University of Windsor, and I previously completed an Electronics Engineering program at St. Clair College. I also worked at Centerline Windsor for a year doing controls and Automation.

I currently work as a Research Assistant at the University investigating lithium batteries and their characteristics. Some research projects I lead or contributed to include: CloudBFG Battery Characterization, HIL Temperature Model, Battery Fuel Gauge Evaluation, and some smaller ones. Additionally, I use VESC as an open source motor controller for a custom-built electric longboard, which is essentially an e-bike motor with a snowboard attached to it, and have tampered with the firmware, and every other component on-board to make it my own.

I have had an interest in batteries and control systems since I was in high school, and have been tinkering since I was 7. This will be a job that I will be passionate about, and I will be able to contribute to the company, and build a career with Stellantis. 

Through this letter, I hope to convey my genuine interest in this position, it is very suited to my interests. I am confident that my skills and experience will make me a valuable asset to your team. I look forward to discussing this opportunity with you further. Thank you for your time and consideration.