% Research Associate, AI for Battery Materials Discovery

My name is Cole, and I am very passionate about anything to do with programming or electronics. My main areas of interest are in Embedded Systems, Machine Learning, Concurrency, and just about anything low-level. I am constantly pursuing personal projects about anything I am interested in, and would always rather be tinkering over playing games. I started at 7 when I got an Electronics Playground for Christmas, and have been obsessed ever since.

I have had an acute interest in batteries since early high school, making it about 8 years since I started tinkering with Lithium. I worked the last two years as a Research Associate at the University of Windsor, where I headed up two major projects and assisted on a number of smaller projects for the BMSLabs team. The primary focus of my research was the mathematical characterization of lithium-ion batteries, as well as AI approaches to characterization using data collected in the field. I have a wide skillset, and feel I would be a great fit for this position, as it would allow me to continue to pursue my passion for batteries, while also allowing me to expand my knowledge in the field of AI.

An example of my related work would be the AI battery characterization algorithm that I developed for my capstone project. It uses a combination of machine learning and signal processing to determine the state of charge, state of health, and state of power of a battery pack. It is currently being used by the University of Windsor's BMSLabs Team to characterize their battery packs for some other projects.