% Research Associate, AI for Battery Materials Discovery

My name is Cole, and I am very passionate about anything to do with batteries, programming or electronics (mainly batteries), making a C++ position at ChargeLabs very appealing. My main areas of interest are in Embedded Systems, Machine Learning, Concurrency, and just about anything low-level. I am constantly pursuing personal projects about anything I am interested in, and would always rather be tinkering over playing games. I started at 7 when I got an Electronics Playground for Christmas, and have been playing with batteries and battery management systems since I was 15.

I have had an acute interest in batteries since early high school, making it about 8 years since I started tinkering with Lithium. I worked the last two years as a Research Associate at the University of Windsor, where I headed up two major projects and assisted on a number of smaller projects for the BMSLabs team. During my time there I made a fork of an open source BMS for testing of estimation algorithms and data collection. The primary focus of my research was the mathematical characterization of lithium-ion batteries using real-world data, as well as AI approaches to characterization using data collected in the field. I have a wide skillset, and feel I would be a great fit for this position, as it would allow me to continue to pursue my passion for batteries and embedded systems.

I would love an interview with ChargeLabs, and I am available to start immediately. I can be reached at \href{mailto:colefuerth@gmail.com}{colefuerth@gmail.com}, or at 519-300-2877. Thank you for your time and consideration, and I look forward to hearing from you.