I am very excited for an opportunity to work on the Ford team! I have a few peers who either work or have worked with Ford, and I already know that I would be an excellent fit for this role. My main interest is in EVs and vehicle controls, so I will have an emotional investment in this position, and can guarantee I will excel at what I do.

I am a software engineer that loves C/C++ and Python! My idea of a fun friday night is watching some suckerpinch videos, "Harder Drives" has got to be my favourite. I have always been at or near the top of all my classes, and was involved academically wherever I could for the community, through tutoring, TAing, or research. The point here being that I have a diverse skillset and will do my best to be as helpful to the rest of the team as I can be. My distro of choice is Pop!\_OS, but this is simply because I enjoy that it is (almost) Ubuntu, but with the System76 repositories for machine learning and gaming. I do live outside Windsor, but am planning to relocate if I can! Some more details about me:

\begin{itemize}
  \item I love EVs and anything robotics related. Embedded systems are my bread and butter, but I would also like to explore the field of Software Engineering, as it would mesh well with my knowledge of both Embedded and Machine Learning.
  \item Mathew Pellarin and I won first place in the Emulators category at CSGames 2023! We also entered in the Machine Learning and Extreme Programming categories for our university, but did not place.
  \item I have been playing with electronics and making things with them since I was 7.
  \item I have built an EV platform from scratch using custom PCBs as my Electronics Engineering Capstone.
  \item I graduated with a Bachelors in Honours Computer Science (AI Specialization) with distinction and a math minor from the University of Windsor, as well as an Electronics Engineering degree from St. Clair College. My GPA for both degrees was around 90\%.
  \item I like motorcycling, electric boarding, rock climbing, coffee, and video games! Most of my hobbies have a DIY component to them, and I love to learn new skills.
%   \item I grew up on a small family farm, where I learned to work with my hands and gained a lot of technical skills. I can (competently) operate all of the heavy equipment, fix the machines in the field, and I am responsible for most of the electrical diagnostics and repairs for everything here. I paired this experience with my Electronics Engineering and Computer Science degrees to make a lot of cool projects. Engines are cool, too!
\end{itemize}
